General constraints on magic distillation protocols from statistical mechanics

### 2021-05-01 magic_paper.tex
minor changes

The bounds also depend on the overlaps between the Hamiltonian eigenbases and the computational basis $\{\ket{k}\}$, where $k \in \mathbb{Z}_d$.
For a reference state $\tau$ with associated Hamiltonian $H$ denote the energy eigenbasis by $\{\ket{\phi_k}\}$ and define the \emph{reference partition function $\zeta$} as
\begin{equation}
	\zeta \coloneqq \sum_{k \in \mathbb{Z}_d} \alpha_k e^{-\beta E_k},
\end{equation}
where the overlap coefficients are
\begin{equation}
	\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_d} \braket{\phi_k}{-r}\braket{r}{\phi_k}.
\end{equation}
Coefficients $\alpha_k$ can be negative when the Hamiltonian $H$ does not admit a Wigner-positive decomposition. 
However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$ - this argument is a bit cyclic}
We can then naturally associate to the reference state $\tau$ a new form of free energy which is specific to the protocol, which we call the \emph{reference free energy $\Phi$} and define via
\begin{equation}
	\Phi \coloneqq -\beta^{-1} \log \zeta.
\end{equation}
For the output reference state $\sigma$ with associated Hamiltonian $H'$, we can denote the energy eigenbasis by $\{\ket{\phi'_k}\}$ and similarly define the reference partition function $\zeta'$ and reference free energy $\Phi'$.

>>>>

The bounds also depend on the overlaps between the Hamiltonian eigenbases and the computational basis $\{\ket{k}\}$, where $k \in \mathbb{Z}_d$.
For a reference state $\tau$ with associated Hamiltonian $H$, denote the energy eigenbasis by $\{\ket{\phi_k}\}$ and define the \emph{reference partition function $\zeta$} as
\begin{equation}
	\zeta \coloneqq \sum_{k \in \mathbb{Z}_d} \alpha_k e^{-\beta E_k},
\end{equation}
where the overlap coefficients are
\begin{equation}
	\alpha_k \coloneqq \sum_{r \in \mathbb{Z}_d} \braket{\phi_k}{-r}\braket{r}{\phi_k}.
\end{equation}
Coefficients $\alpha_k$ can be negative when the Hamiltonian $H$ does not admit a Wigner-positive decomposition. 
However, it is simple to see that $\zeta$ is always positive. \nick{because it is proportional to $W_{\tau}(0,0) > 0$ for full-rank, stabilizer $\tau$}
We can then naturally associate to the reference state $\tau$ a new form of free energy which is specific to the protocol, which we call the \emph{reference free energy $\Phi$} and define via
\begin{equation}
	\Phi \coloneqq -\beta^{-1} \log \zeta.
\end{equation}
For the output reference state $\sigma$ with associated Hamiltonian $H'$, we can denote the energy eigenbasis by $\{\ket{\phi'_k}\}$ and similarly define the reference partition function $\zeta'$ and reference free energy $\Phi'$.
